### 2009-11-29 doc/tech_doc/janitor/tex_titlepage/titlepage.tex
Having symbolic link helping the merge process.

\def\today{\number\day/\number\month/\number\year}

\begin{titlepage}

\begin{tabular}{rl}
\resizebox*{3cm}{!}{\includegraphics{ng-logo.png}}
&\parbox[b]{2cm}{\textbf \it {\hspace*{-1.5cm}NORDUGRID\vspace*{0.5cm}}}
\end{tabular}

\hrulefill

{\raggedleft NORDUGRID-D2.5-2 ???\par}

{\raggedleft \today\par}

\vspace*{2cm}

%%%%---- The title ----
{\centering \textsc{\Large Dynamic Runtime Environment Installation with Janitor}
\\\vspace{1cm} \normalsize\textcolor{discreeturgent}{The Janitor and this document with it is under continuous development. Your comments and suggestions are appreciated.} % DELETE ONLY THAT LINE!!!
\Large \par}
\vspace*{0.5cm}

%%%%---- A subtitle, if necessary ----
%{\centering \textit{\large Paper subtitle}\large \par}

\vspace*{1.5cm}
%%%%---- A list of authors ----
    {\centering \large Michael Glodek, Daniel Bayer,  Steffen M\"oller\footnote{moeller@inb.uni-luebeck.de} \par}

%%%%---- An abstract - if style is article ----
%\begin{abstract}
%The abstract
%\end{abstract}
\end{titlepage}

\tableofcontents                          %Comment if use article style
\newpage
%\chapter{Preface}
%\section{Introduction}                    %Use Sections for articles
%\label{sec:intro}

\sloppy

>>>>

../../../manuals/janitor/tex_titlepage/titlepage.tex
